Dependent Object Types

### 2012-08-08 article.tex
todos

In the calculus we made the deliberate choice not to model any form of
inheritance. This is, first and foremost, to keep the calculus simple.
Secondly, there are many different approaches to inheritance and
mixin composition, so that it looks advantageous not to tie the basic
calculus to a specific one. Finally, it seems that the modelization of
inheritance lends itself to a different approach than the basic
calculus. For the latter, we need to prove type safety of the calculus.
One might try to do this also for a calculus with inheritance, but our
experience suggests that this complicates the proofs considerably.  An
alternative approach to inheritance that might work better is to model
it as a form of code-reuse. Starting with an enriched type system with
inheritance, and a translation to the basic calculus, one needs to
show type safety wrt the translation. This might be easier than
to prove type safety wrt reduction.

\remark{Does this last point still makes sense wrt to type safety via
  logical relations instead of via the standard theorems of
  preservation and progress?}

@@

\todo{more discussion subsections?}

\section{Conclusion}\label{conclusion}
\todo{conclusion}

@@

\acks
\todo{acks}

>>>>

In the calculus we made the deliberate choice not to model any form of
inheritance. This is, first and foremost, to keep the calculus simple.
Secondly, there are many different approaches to inheritance and
mixin composition, so that it looks advantageous not to tie the basic
calculus to a specific one. Finally, it seems that the modelization of
inheritance lends itself to a different approach than the basic
calculus. For the latter, we need to prove type safety of the calculus.
One might try to do this also for a calculus with inheritance, but our
experience suggests that this complicates the proofs considerably.  An
alternative approach that might work better is to model inheritance
it as a form of code-reuse. Starting with an enriched type system with
inheritance, and a translation to the basic calculus, one needs to
show type safety wrt the translation. This might be easier than
to prove type safety wrt reduction.

@@

\section{Conclusion}\label{conclusion}

@@

\acks

We thank Amal Ahmed for her many discussions and insights about
applying logical relations to DOT. We thank Donna Malayeri and
Geoffrey Washburn for preliminary work on DOT.
